---
title: "Data Sources"
output: 
  github_document:
    html_preview: false
---

```{r setup, include=FALSE}
# included by default in the R Markdown template
knitr::opts_chunk$set(echo = TRUE)
# set working directory; knitr defaults to loc of .Rmd file
knitr::opts_knit$set(root.dir = here::here())
```

## `state-legislatures`

I downloaded these data from https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/6QWX7Q on 2018-07-29.

The raw data include three files, which I retain in the project files:

* The original data set: `data/raw/shor_mccarty_1993-2016_individual_legislator_data_May_2018_release_(Updated_July_2018).dta`. The filename originally had spaces. I replaced each space with an `_` to facilitate more robustness in computing.
* The latest codebook: `data/raw/shor mccarty state legislator data codebook may 2018-1.pdf`
* The orginal artile: `data/raw/shor and mccarty 2011 final apsr.pdf`

```{r, message=FALSE}
# load packages
library(tidyverse)
library(haven)

# take glimpse at raw data 
read_dta("data/raw/shor_mccarty_1993-2016_individual_legislator_data_May_2018_release_(Updated_July_2018).dta") %>%
  glimpse()
```

Dataverse suggested the following citation:
```
@data{DVN/6QWX7Q_2018,
author = {Shor, Boris},
publisher = {Harvard Dataverse},
title = {Individual State Legislator Shor-McCarty Ideology Data, May 2018 update},
year = {2018},
doi = {10.7910/DVN/6QWX7Q},
url = {https://doi.org/10.7910/DVN/6QWX7Q}
}
```

The R script `R/clean-data.R` tidies the raw data set into a cleaned `.csv` and `.rds` versions. The variable names sufficiently describe most variables. Shor and McCarty (2011) explain the `ideology` variable.

```{r}
# take glimpse at cleaned .csv data 
read_rds("data/shor-mccarty.rds") %>%
  glimpse()
```



